%-----------------------------------------------------
% Stuart WD Grieve CV
%
% Based on Simon M. Mudd's CV: github.com/simon-m-mudd/CV_SMudd/
%
% This CV is loosely based on the template produced by
% Dario Taraborelli
% URL: http://nitens.org/taraborelli/cvtex
%----------------------------------------------------

% !TEX program = xelatex
%!TEX encoding = UTF-8 Unicode

\documentclass[10pt, a4paper]{article}
\usepackage{fontspec}

% DOCUMENT LAYOUT
\usepackage{geometry}
\geometry{a4paper, textwidth=5.75in, textheight=9.5in, marginparsep=7pt, marginparwidth=.6in}
\setlength\parindent{0in}

%FONTS
\usepackage{xunicode}
\usepackage{xltxtra}
\defaultfontfeatures{Mapping=tex-text} % converts LaTeX specials (``quotes'' --- dashes etc.) to unicode
%For gentium, you should install the font from here: http://scripts.sil.org/cms/scripts/page.php?site_id=nrsi&item_id=Gentium_basic
%\setromanfont [Ligatures={Common}, BoldFont={Gentium Basic Bold}, ItalicFont={Gentium Basic Italic}]{Gentium Basic}

%For fontin font, you should install the font from here: http://www.exljbris.com/fontin.html
%\setromanfont [Ligatures={Common}, BoldFont={Fontin Bold}, ItalicFont={Fontin Italic}]{Fontin}

%For linux libertine font, you should install from fontsquirrel, http://www.fontsquirrel.com/
% This one seems to be happiest! Least bad boxes. And looks nice
%\setromanfont [Ligatures={Common}, BoldFont={Linux Libertine Bold}, ItalicFont={Linux Libertine Italic}]{Linux Libertine}

%For Liberation Serif font, you should install from fontsquirrel, http://www.fontsquirrel.com/
%\setromanfont [Ligatures={Common}, BoldFont={Liberation Serif Bold}, ItalicFont={Liberation Serif Italic}]{Liberation Serif}

%For Heuristica Serif font, you should install from fontsquirrel, http://www.fontsquirrel.com/
% This one also seems to make XeLaTeX happy
\setromanfont [Ligatures={Common}, BoldFont={Heuristica Bold}, ItalicFont={Heuristica Italic}]{Heuristica}

%\setmonofont[Scale=0.8]{Heuristica}

\usepackage{fontawesome5}
\usepackage{academicons}

% ---- CUSTOM COMMANDS
\chardef\&="E050
\newcommand{\html}[1]{\href{#1}{\scriptsize\textsc{[html]}}}
\newcommand{\pdf}[1]{\href{#1}{\scriptsize\textsc{[pdf]}}}
\newcommand{\doi}[1]{\href{https://dx.doi.org/#1}{\scriptsize\textsc{[URL]}}}
\newcommand{\bib}[1]{\href{https://www.doi2bib.org/bib/#1}{\scriptsize\textsc{[BibTeX]}}}
\newcommand{\paperlinks}[1]{\doi{#1} \bib{#1}}
\newcommand{\student}{\textbf{\textsuperscript{\textdagger}}}

% ---- MARGIN YEARS
\usepackage{marginnote}
\newcommand{\amper{}}{\chardef\amper="E0BD }
\newcommand{\years}[1]{\marginnote{\scriptsize #1}}
\renewcommand*{\raggedleftmarginnote}{}
\setlength{\marginparsep}{7pt}
\reversemarginpar

% HEADINGS
\usepackage{sectsty}
\usepackage[normalem]{ulem}
\sectionfont{\mdseries\upshape\Large}
\subsectionfont{\mdseries\scshape\normalsize}
\subsubsectionfont{\mdseries\upshape\large}

\newcommand{\MONTH}{%
  \ifcase\the\month
  \or January% 1
  \or February% 2
  \or March% 3
  \or April% 4
  \or May% 5
  \or June% 6
  \or July% 7
  \or August% 8
  \or September% 9
  \or October% 10
  \or November% 11
  \or December% 12
  \fi}

%columns
\usepackage{multicol}
\setlength{\columnsep}{10pt}
%\def\columnseprulecolor{\color{White}}

% PDF SETUP
% ---- FILL IN HERE THE DOC TITLE AND AUTHOR
\usepackage[bookmarks, colorlinks, breaklinks,
% ---- FILL IN HERE THE TITLE AND AUTHOR
	pdftitle={Stuart W D Grieve - cv},
	pdfauthor={Stuart W. D. Grieve},
]{hyperref}
\hypersetup{linkcolor=blue,citecolor=blue,filecolor=black,urlcolor=blue}

%Colours
\usepackage[usenames,dvipsnames]{xcolor}
\definecolor{Gray}{rgb}{0.3,0.3,0.3}
\definecolor{LightGray}{rgb}{0.6,0.6,0.6}

% Header and footer
\usepackage{fancyhdr}
\pagestyle{fancy}
\fancyhf{}
\rhead{\textcolor{LightGray}{SWD Grieve -- \MONTH \ \the\year}}
\renewcommand{\footrulewidth}{1pt}
\rfoot{\textcolor{LightGray}{Page \thepage}}

%urls
\usepackage{url}

% DOCUMENT
\begin{document}

{\LARGE Stuart William David Grieve}\\
\textcolor{Gray}{\large{Reader in Physical Geography}}

\begin{multicols}{2}
School of Geography\\
Queen Mary University of London\\
Mile End Road\\
London, E1 4NS\\
United Kingdom

\columnbreak
\vspace*{-24pt} % Hard coded value of 2 * the line height \baselineskip
\faPhone \ \ \texttt{+44~(0)20~7882~2780}\\
\faEnvelope \ \ \href{mailto:s.grieve@qmul.ac.uk}{s.grieve@qmul.ac.uk}\\
\faGithub \ \ \href{https://github.com/sgrieve}{sgrieve}\\
\aiGoogleScholar \ \ \href{https://scholar.google.co.uk/citations?user=VwQbAzQAAAAJ&hl=en}{Stuart W D Grieve}\\
\aiOrcid \ \ \href{https://orcid.org/0000-0003-1893-7363}{0000-0003-1893-7363}\\
\faGlobe \ \ \href{http://swdg.io/}{swdg.io/}

\end{multicols}

\hrule
\section*{Appointments}
\noindent

\years{2024--} \textbf{Reader in Physical Geography}, Queen Mary University of London\\[0.05cm]
\years{2021--} \textbf{Fellow of the Digital Environment Research Institute}, Queen Mary University of London\\[0.05cm]
\years{2021--2024} \textbf{Senior Lecturer in Physical Geography}, Queen Mary University of London\\[0.05cm]
\years{2018--2021} \textbf{Lecturer in Physical Geography}, Queen Mary University of London\\[0.05cm]
\years{2017--2018} \textbf{Research Software Developer}, University College London\\[0.05cm]
\years{2017} \textbf{Lecturer in Physical Geography}, Queen Mary University of London\\[0.05cm]
\years{2016--2017} \textbf{Postdoctoral Research Associate}, University of Edinburgh\\[0.05cm]
\textit{Topographic analysis and landslide modelling software.}\\[0.05cm]
\years{2016} \textbf{Research Assistant}, Cardiff University\\[0.05cm]

\hrule
\section*{Education}
\noindent

\years{2018--2020}\textbf{Postgraduate Certificate Academic Practice (PGCAP)} Queen Mary University of London\\[0.05cm]

\years{2013--2016}\textbf{Ph.D. in Atmospheric and Environmental Sciences} University of Edinburgh\\[0.05cm]
\textit{Uncovering signatures of geomorphic process through high resolution topography.}\\[0.05cm]
Supervisors: Professor Simon M Mudd and Dr Tristram C Hales (Cardiff University)\\

\years{2011--2012}\textbf{M.Sc. in Geographical Information Science} (Distinction) University of Edinburgh\\[0.05cm]
Thesis Title: \textit{An automated analysis of the southern San Andreas Fault to explore topography’s relationship with tectonics.}\\[0.05cm]
Supervisor: Professor Simon M Mudd\\

\years{2007--2011}\textbf{B.Sc. (Hons.) in Geology and Physical Geography} (2:1) University of Edinburgh\\[0.05cm]
Thesis Title: \textit{The Influence of Climate Change on Landslide Sediment Yields in the Northern Lake District.}\\[0.05cm]

\hrule
\section*{Awards}
\noindent

\textbf{QMUL Faculty Awards}\\[0.05cm]
\years{2023} Excellence in Postgraduate Researcher Support \textit{nominee} \\[0.05cm]
\years{2023} Digital teacher of the year \textit{nominee} \\[0.05cm]

\textbf{QMUL Education Awards}\\[0.05cm]
\years{2021} Online Learning Champion \textit{nominee} \\[0.05cm]
\years{2021} Assessment and Feedback Champion \textit{nominee} \\[0.05cm]
\years{2021} Innovative Use of Technology Award \textit{nominee} \\[0.05cm]
\years{2019} Innovative Teaching Award \textit{nominee} \\[0.05cm]
\years{2019} Technology Enhanced Learning Award \textit{nominee} \\[0.05cm]
\years{2019} Teacher of the Year \textit{nominee} \\[0.05cm]

\years{2018}\textbf{Software Sustainability Institute Fellowship}\\[0.05cm]
Awarded to support my work developing sustainable geoscience software\\[0.05cm]

\years{2017}\textbf{Wiley Award} from the British Society for Geomorphology\\[0.05cm]
Awarded for the best paper published in \textit{Earth Surface Processes and Landforms} in 2016\\[0.05cm]

\hrule
\section*{Ph.D. Student Supervision}
\noindent

\years{2025--} \textbf{Billy Newman} QMUL Principal's Studentship: \textit{Understanding the Geomorphological Characteristics of Anthropogenic Coasts.}\\[0.05cm]
\years{2024--} \textbf{Desmond Teh} Cambridge Trusts: \textit{Improving rainfall interception estimation with combined drone and terrestrial LiDAR data in forested areas.}\\[0.05cm]
\years{2024--} \textbf{Graeme Erskine} AHRC Studentship: \textit{A computer-based analysis of the Roman Roads of Northern Britain.}\\[0.05cm]
\years{2024--} \textbf{Tom Hoseason} NERC London DTP Studentship: \textit{Quantifying interactions between topographic variability and forest structure.}\\[0.05cm]
\years{2024--} \textbf{Laura Molares Moncayo} Human Frontiers Science Programme Studentship: \textit{The Role of the Atmosphere in Shaping and Sustaining Microbial Communities on Glaciers.}\\[0.05cm]
\years{2022--} \textbf{Owen James} NERC London DTP Studentship: \textit{Shoreline and Beach Volumetric Change Assessment and Prediction Using Machine Learning Techniques.}\\[0.05cm]
\years{2021--} \textbf{Stefan Baternay} QMUL Principal's Studentship: \textit{High resolution topographic analysis to reconstruct Martian landscape evolution.}\\[0.05cm]
\years{2021--} \textbf{Matt Allen} UKRI AI4ER CDT: \textit{Automated tree species classification from forest Terrestrial Laser Scanning Data.}\\[0.05cm]
\years{2020-2024} \textbf{Nan Wu} Lloyds Register Foundation: \textit{Fate and behaviour of microplastics in the natural environment.} Now a Postdoc at British Antarctic Survey.\\[0.05cm]
\years{2020--} \textbf{Shudan Xue} China Scholarship Council Studentship: \textit{Erosion of Coastal Historic Landfills – Waste Release from East Tilbury landfill.}\\[0.05cm]
\years{2020-2024} \textbf{William Flynn} NERC London DTP Studentship: \textit{Novel High-Resolution Three-Dimensional Mapping of Vegetation Using Unmanned Aerial Vehicles (UAV) and Structure from Motion Photogrammetry (SfM).} Now a Postdoc at the University of Cambridge.\\[0.05cm]
\years{2020-2021} \textbf{Harry Owen} NERC London DTP Studentship: \textit{Climate Change and Biomass Dynamics: Novel Methods in Extracting Forest Biophysical Properties.} Now a Postdoc at the University of Cambridge.\\[0.05cm]

\hrule
\section*{Postdoctoral Research Supervision}
\noindent

\years{2022-2024} \textbf{Milto Miltiadou} UKRI FLF tied PDRA: \textit{Next generation forest dynamics modelling using remote sensing data.} Now a Lecturer in Computer Science at The University of Exeter.\\[0.05cm]
\years{2021--} \textbf{Harry Owen} UKRI FLF tied PDRA: \textit{Next generation forest dynamics modelling using remote sensing data.}\\[0.05cm]


% Setting up conditionals so we can either show or hide the statements in the cv
% Will throw errors if not built using build.sh
\iflong

  \hrule
  \section*{Research Statement}
  \noindent

  My research aims to develop an understanding of how signals of change, such as those driven by tectonics or the environment, manifest in the surface morphology of the Earth and other planetary bodies. In particular, I aim to bridge the gap between numerical models, remotely sensed data and field observations and I conduct such research through the development of open source software which facilitates reproducible analysis, with a particular focus on the processing of high resolution topographic data. Such software allows repeatable experiments to be performed on both terrestrial and planetary landscapes, at a range of scales spanning individual hillslopes to continental scale features. I also work on the development and application of cutting edge GIS and computer science techniques to enhance surface process research, through the analysis of complex spatial information combined with novel data collection approaches and high performance computing.\\[0.05cm]

  \hrule
  \section*{Teaching Statement}
  \noindent

  My teaching, as with my research, focuses on the implementation and application of quantitative and computational methods, as a framework to understand Earth surface processes. I am passionate about engaging students to interpret landscapes and the processes which act upon them both in a classroom and field setting. I have experience of teaching theoretical and applied GIS, either within the context of physical geography or a number of other disciplines (transport planning, infrastructure, crime research, archaeology) at both an undergraduate and postgraduate level. Aside from teaching physical geography and GIS, I also enjoy teaching scientific programming to students, giving them a grounding in data analysis and visualisation which can be employed throughout their time in education and beyond. Such skills are vital for students and I believe I am well placed to teach these skills within a physical science context.\\[0.05cm]

\fi

\hrule
\section*{Media}
\noindent

\years{2023}Landfills: Britain's Toxic Secrets. \textbf{BBC Panorama.} Broadcast 22/05/2023.\\[0.05cm]

\hrule
\section*{Other Employment}
\noindent

\years{2015--2016} \textbf{GIS Consultant and Field Course Leader}, GeoBus, University of St Andrews\\[0.05cm]
\years{2012--2013} \textbf{GIS Trainee} Forth Crossing Bridge Constructors\\[0.05cm]

\hrule
\section*{Publications}
\noindent
\student denotes student author.\\[0.05cm]

\years{Accepted}\textbf{Grieve, S.W.D.}, Singer, M.B., Chen, S-a, Michaelides, K., \textit{GDBM: A database of global drainage basin morphology.} PLOS ONE\\[0.05cm]

\years{Accepted}Miltiadou, M., \textbf{Grieve, S.W.D.}, Ruiz-Benito, P., Astigarraga, J., Cruz-Alonso, V., Trivi\~{n}o, J.T, Lines, E.R., \textit{PlotToSat: A Tool for Generating Time-series Signatures from Sentinel-1 and Sentinel-2 at 3 at field-based plots for Machine Learning applications.} Environ. Model. Softw.\\[0.05cm]

\years{Accepted}Karg\'ere, B.A.\student, Hales, T.C., Constantine, J.A., \textbf{Grieve, S.W.D.}, Johnson, S.D., \textit{A Fractal Framework for Channel-Hillslope Coupling.} Earth Surf. Dynam. \paperlinks{10.5194/egusphere-2024-2847}\\[0.05cm]

\years{2025}Wu, N\student, \textbf{Grieve, S.W.D.}, Manning, A.J, Spencer K.L., \textit{Marine snow as vectors for microplastic transport: Multiple aggregation cycles account for the settling of buoyant microplastics to deep-sea sediments.} Limnol. Oceanogr. \paperlinks{10.1002/lno.12814}\\[0.05cm]

\years{2024}Singer, M.B., \textbf{Grieve, S.W.D.}, Chen, S-a, Michaelides, K., \textit{Climatic Controls on the Length and Shape of the World's Drainage Basins.} Geophys. Res. Lett. \paperlinks{10.1029/2024GL111220}\\[0.05cm]

\years{2024}Wu, N\student, \textbf{Grieve, S.W.D.}, Manning, A.J, Spencer K.L., \textit{Flocs as vectors for microplastics in the aquatic environment.} Nat. Water \paperlinks{10.1038/s44221-024-00332-4}\\[0.05cm]

\years{2024}Allen, M.J.\student, Moreno-Fern\'andez, D., Ruiz-Benito, P., \textbf{Grieve, S.W.D.}, Lines, E.R., \textit{Low-cost tree crown dieback estimation using deep learning-based segmentation.} Environmental Data Science. \paperlinks{10.1017/eds.2024.16}\\[0.05cm]

\years{2024}Miltiadou, M., Lines, E.R., \textbf{Grieve, S.W.D.}, Ruiz-Benito, P., Astigarraga, J., Cruz, V., \textit{Tree genera classifications in Spain using time-series Sentinel-2 data extracted from PlotToSat.} IEEE International Geoscience and Remote Sensing Symposium.\paperlinks{10.1109/IGARSS53475.2024.10641135}\\[0.05cm]

\years{2024}Flynn, W.R.M\student, \textbf{Grieve, S.W.D.}, Henshaw, A.J., Owen, H.J.F., Buggs, R.J.A, Metheringham, C.L., Plumb, W.J., Stocks, J.J, Lines, E.R., \textit{UAV-derived greenness and within-crown spatial patterning can detect ash dieback in individual trees.} Ecol. Solut. Evid. \paperlinks{10.1002/2688-8319.12343} \\[0.05cm]

\years{2024}James, O.C.\student, Schillereff, D.N., \textbf{Grieve, S.W.D.}, Baas, A.C.W., \textit{PyShoreVolume 1.0.0: A Python based Shoreline Change and beach Volumetric Change Analysis tool.} Comput. Geosci. \paperlinks{10.1016/j.cageo.2024.105591} \\[0.05cm]

\years{2023}Flynn, W.R.M\student, Owen, H.J.F., \textbf{Grieve, S.W.D.}, Lines, E.R., \textit{Quantifying vegetation indices using TLS: methodological complexities and ecological insights from a Mediterranean forest.} Biogeosciences.\paperlinks{10.5194/bg-20-2769-2023} \\[0.05cm]

\years{2022}Chen, S-a, Michaelides, K., \textbf{Grieve, S.W.D.}, Singer, M.B., \textit{Reply to: Climate versus tectonics as controls on river profiles.} Nature. \paperlinks{10.1038/s41586-022-05419-0}\\[0.05cm]

\years{2022}Lines, E.R., Allen, M.J.\student, Cabo, C., Calders, K., Debus, A., \textbf{Grieve, S.W.D.}, Miltiadou, M., Noach, A., Owen, H.J.F., Puliti, S., \textit{AI applications in forest monitoring need remote sensing benchmark datasets.} Big Data Analytics for Sustainability 2022.\paperlinks{10.48550/arXiv.2212.09937}\\[0.05cm]

\years{2022}Allen, M.J.\student, \textbf{Grieve, S.W.D.}, Owen, H.J.F., Lines, E.R., \textit{Tree species classification from complex laser scanning data in Mediterranean forests using deep learning} Methods Ecol. Evol. \paperlinks{10.1111/2041-210X.13981}\\[0.05cm]

\years{2021}Gailleton, B., Mudd, S.M., Clubb, F.J., \textbf{Grieve, S.W.D.}, Hurst, M.D., \textit{Impact of changing concavity indices on channel steepness and divide migration metrics.} J. Geophys. Res. Earth Surf. \paperlinks{10.1029/2020JF006060}\\[0.05cm]

\years{2021}Gabet, E.J., Mudd, S.M., Wood, R.W., \textbf{Grieve, S.W.D.}, Binnie, S.A., Dunai, T.J., \textit{Hilltop Curvature Increases with the Square Root of Erosion Rate.} J. Geophys. Res. Earth Surf. \paperlinks{10.1029/2020JF005858}\\[0.05cm]

\years{2020} \textbf{Grieve, S.W.D.}, Clubb, F.J., Mudd, S.M., \textit{Reproducible topographic analysis.} In Tarolli, P., Mudd S.M. (Ed.) Remote Sensing of Geomorphology. \paperlinks{10.1016/B978-0-444-64177-9.00012-6}\\[0.05cm]

\years{2020} Clubb, F.J., Mudd, S.M., Hurst, M.D., \textbf{Grieve, S.W.D.}, \textit{Differences in channel and hillslope geometry record a migrating uplift wave at the Mendocino Triple Junction.} Geology. \paperlinks{10.1130/G46939.1}\\[0.05cm]

\years{2019}Chen, S-a, Michaelides, K., \textbf{Grieve, S.W.D.}, Singer, M.B., \textit{Aridity is expressed in river topography globally.} Nature. \paperlinks{10.1038/s41586-019-1558-8}\\[0.05cm]

\years{2019} Hurst, M.D., \textbf{Grieve, S.W.D.}, Mudd, S.M., Clubb, F.J., \textit{Detection of channel-hillslope coupling along a tectonic gradient.} Earth Planet. Sci. Lett. \paperlinks{10.1016/j.epsl.2019.06.018}\\[0.05cm]

\years{2018}\textbf{Grieve, S.W.D.}, Hales, T.C., Parker, R.N, Mudd, S.M., Clubb, F.J., \textit{Controls on zero-order basin morphology.} J. Geophys. Res. Earth Surf. \paperlinks{10.1029/2017JF004453}\\[0.05cm]

\years{2017}\textbf{Grieve, S.W.D.}, \textit{spatial-efd: A spatial-aware implementation of elliptical Fourier analysis.} J. Open Source Softw. \paperlinks{10.21105/joss.00189}\\[0.05cm]

\years{2016}\textbf{Grieve, S.W.D.}, Mudd, S.M., Hurst, M.D., \textit{How long is a hillslope?} Earth Surf. Process. Landforms. \paperlinks{10.1002/esp.3884}\\[0.05cm]

\years{2016}\textbf{Grieve, S.W.D.}, Mudd, S.M., Hurst, M.D., Milodowski, D.T., \textit{A nondimensional framework for exploring the relief structure of landscapes.} Earth Surf. Dynam. \paperlinks{10.5194/esurf-4-309-2016}\\[0.05cm]

\years{2016}\textbf{Grieve, S.W.D.}, Mudd, S.M., Milodowski, D.T., Clubb, F.J., Furbish, D.J., \textit{How does grid-resolution modulate the topographic expression of geomorphic processes?} Earth Surf. Dynam. \paperlinks{10.5194/esurf-4-627-2016}\\[0.05cm]

\years{2016}Parker, R.N., Hales, T.C., Mudd, S.M., \textbf{Grieve, S.W.D.}, Constantine, J.A., \textit{Colluvium supply in humid regions limits the frequency of storm-triggered landslides.} Sci. Rep. \paperlinks{10.1038/srep34438}\\[0.05cm]

\years{2016}Mudd, S. M., Harel, M.-A., Hurst, M. D., \textbf{Grieve, S.W.D.}, and Marrero, S. M., \textit{The CAIRN method: Automated, reproducible calculation of catchment-averaged denudation rates from cosmogenic radionuclide concentrations}, Earth Surf. Dynam. \paperlinks{10.5194/esurf-4-655-2016}\\[0.05cm]

\years{2016}Clubb, F.J., Mudd. S.M., Attal, M., Milodowski, D.T., and \textbf{Grieve, S.W.D.}, \textit{The relationship between drainage density, erosion rate, and hilltop curvature: implications for sediment transport processes}, J. Geophys. Res. Earth Surf. \paperlinks{10.1002/2015JF003747}\\[0.05cm]

\years{2014}Mudd, S.M., Attal, M., Milodowski, D.T., \textbf{Grieve, S.W.D.}, Valters, D.A., \textit{A statistical framework to quantify spatial variation in channel gradients using the integral method of channel profile analysis.} J. Geophys. Res. Earth Surf. \paperlinks{10.1002/2013JF002981}\\[0.05cm]

\hrule
\section*{Conference Presentations}

\subsection*{Invited Talks}

\years{2025}\textbf{Grieve, S.W.D.}, \textit{Forest-landscape dynamics: Terrestrial Laser Scanning as a tool to link forest structure and landscape form in 3D.} Presented at The School of GeoSciences, University of Edinburgh.\\[0.05cm]

\years{2024}\textbf{Grieve, S.W.D.}, \textit{Forest-landscape dynamics: Terrestrial Laser Scanning as a tool to link forest structure and landscape form in 3D.} Presented at The Department of Geography, University of Durham.\\[0.05cm]

\years{2019}\textbf{Grieve, S.W.D.}, \textit{Lasers, landslides and bendy bananas.} Presented at The School of Geography, Queen Mary University of London.\\[0.05cm]

\years{2017}\textbf{Grieve, S.W.D.}, \textit{Geomorphic insight from high resolution topography: Is it reproducible?} Wiley Award Keynote Lecture, BSG Annual General Meeting, Hull\\[0.05cm]

\years{2016}\textbf{Grieve, S.W.D.}, \textit{Uncovering signatures of geomorphic process through high resolution topography.} Presented at The Hutton Club, University of Edinburgh.\\[0.05cm]

\years{2015}\textbf{Grieve, S.W.D.}, \textit{Reproducible geographic analysis: Insights from geomorphology.} Presented at GIS Update, Edinburgh.\\[0.05cm]

\subsection*{Oral Presentations}

\years{2024}Allen, M.J.\student, Owen, H.J.F., Disney, M., Wilkes, P., \textbf{Grieve, S.W.D.}, Lines, E.R., \textit{Large-Scale Self-Supervised Learning on Forest Point Cloud Data.} Presented at the AGU Fall Meeting, Washington, D.C. \\[0.05cm]

\years{2024} Karg\'ere, B.\student, Hales, T.C., Constantine J.A., \textbf{Grieve, S.W.D.}, \textit{A Fractal Framework for Channel-Hillslope Coupling.} Presented at the AGU Fall Meeting, Washington, D.C. \\[0.05cm]

\years{2024}\textbf{Grieve, S.W.D.}, Owen, H.J.F., Ruiz-Benito, P., Lines, E.R., \textit{Terrestrial laser scanning for forest geomorphology.} Presented at the BSG Annual Meeting, Loughborough.\\[0.05cm]

\years{2024} James, O.C.\student, Schillereff, D.N., \textbf{Grieve, S.W.D.}, \textit{The application of webcams to create high-frequency digital elevation models of the intertidal zone.} Presented at the BSG Annual Meeting, Loughborough.\\[0.05cm]

\years{2024}\textbf{Grieve, S.W.D.}, Owen, H.J.F., Ruiz-Benito, P., Lines, E.R., \textit{Forest-landscape dynamics across a climate gradient.} Presented at the EGU General Assembly, Vienna.\\[0.05cm]

\years{2024}Wu, N.\student, \textbf{Grieve, S.W.D.}, Manning, A.J., Spencer, K.L., \textit{Modelling the sedimentation of macro-, micro- and nanoplastics in the ocean from surface to sediment.} Presented at the EGU General Assembly, Vienna.\\[0.05cm]

\years{2024}Baternay, S.A\student, \textbf{Grieve, S.W.D.}, Wharton, G., Grindrod, P.M., Davis, J.M, \textit{Quantifying Martian Hillslope Variability.} Presented at the Lunar and Planetary Science Conference, Texas.\\[0.05cm]

\years{2023}Wu, N.\student, \textbf{Grieve, S.W.D.}, Manning, A.J., Spencer, K.L., \textit{The Longevity of Plastic Waste at the Ocean Surface.} Presented at the AGU Fall Meeting, San Francisco.\\[0.05cm]

\years{2023}Flynn, W.R.M\student, \textbf{Grieve, S.W.D.}, Henshaw, A.J., Owen, H.J.F., Lines, E.R., \textit{Bridging the gap between earth observation and forest ecology.} Presented at SilviLaser 2023, London.\\[0.05cm]

\years{2023}Allen, M.J.\student, Noach, A., Owen, H.J.F, \textbf{Grieve, S.W.D.}, Lines, E.R., \textit{Efficient 3D Forest Point Cloud Data Processing: Self-Supervised Learning Strategies to Diminish Manual Labeling.} Presented at SilviLaser 2023, London.\\[0.05cm]

\years{2023}Lines, E.R., \textbf{Grieve, S.W.D.}, Owen, H.J.F, Ruiz-Benito, P., \textit{The structural properties of trees and forests in Europe.} Presented at SilviLaser 2023, London.\\[0.05cm]

\years{2023}\textbf{Grieve, S.W.D.}, Owen, H.J.F., Miltiadou, M., Lines, E.R., \textit{Building \lq good enough\rq~digital workflows in the field.} Presented at RSLondonSouthEast 2023, London.\\[0.05cm]

\years{2023} Lines, E.R., Flynn W.R.M\student, \textbf{Grieve, S.W.D.}, Ruiz-Benito, P., \textit{Comparison of extracted ecological features of forests from multiple 3D technologies.} Presented at the EGU General Assembly, Vienna.\\[0.05cm]

\years{2023}Wu, N.\student, \textbf{Grieve, S.W.D.}, Manning, A.J., Spencer, K.L., \textit{Aquatic Aggregates as \lq Vector\rq~ for Microplastics.} Presented at the EGU General Assembly, Vienna.\\[0.05cm]

\years{2022} Flynn W.R.M\student, \textbf{Grieve, S.W.D.}, Henshaw, A.J., Lines, E.R., \textit{Quantifying the impact of Ash Dieback in individual tree crowns using multi-temporal UAV RGB 3D data.} Presented at the British Ecological Society Annual Meeting, Edinburgh.\\[0.05cm]

\years{2022}Wu, N.\student, Spencer, K.L., \textbf{Grieve, S.W.D.}, Manning, A.J., \textit{The Estuary as a Natural Water Treatment Plant for Microplastics.} Presented at the EGU General Assembly, Vienna.\\[0.05cm]

\years{2021}Owen, H.J.F, \textbf{Grieve, S.W.D.}, Lines, E.R., \textit{Three-dimensional structural plasticity in Mediterranean forests.} Presented at the British Ecological Society Annual Meeting, Liverpool.\\[0.05cm]

\years{2021}Wu, N.\student, Spencer, K.L., \textbf{Grieve, S.W.D.}, Manning, A.J., \textit{A systematic study on the interaction between microplastics and cohesive sediments.} Presented at INTERCOH 2021, Online.\\[0.05cm]

\years{2020}Heppell C.M., Bartlett, A., Beechey, A., Jennings, P., Soteriou, H., Rhys, H., Schaefer, B., Beck, C., Treves, R., \textbf{Grieve, S.W.D.}, Wu, Y., Haklay, M., Dinnadge, R., Wishart, J., \textit{ChessWatch: An on-line observatory for the River Chess.} Presented at the British Ecological Society Aquatic SIG Annual Meeting, Online.\\[0.05cm]

\years{2019}\textbf{Grieve, S.W.D.}, Singer, M.B., Chen, S-a, Michaelides, K., \textit{Understanding rivers using the Space Shuttle, LSDTopoTools and HPC.} Presented at RSLondonSouthEast 2019, London.\\[0.05cm]

\years{2018}Singer, M.B., \textbf{Grieve, S.W.D.}, Chen, S-a, Michaelides, K., \textit{Climatic Signatures Within the World’s Rivers.} Presented at the AGU Fall Meeting, Washington, D.C.\\[0.05cm]

\years{2018}Clubb, F.J., Mudd, S.M., Hurst, M.D., \textbf{Grieve, S.W.D.}, \textit{Tectonics vs. eustasy: fluvial terraces, channel profiles, and hillslopes at the Mendocino Triple Junction, California} Presented at the EGU General Assembly, Vienna.\\[0.05cm]

\years{2018}Alegre, R., Georgoulas, A., \textbf{Grieve, S.W.D.}, Robson, E., \textit{Democratizing ancient Mesopotamian research through digital scholarship} Presented at the IEEE 14th International Conference on e-Science, Amsterdam.\\[0.05cm]

\years{2017}Mason, L., Hetherington, J., O'Reilly, M., Yong, M., Jersakova, R., \textbf{Grieve, S.W.D.}, Perez-Suarez, D., Klapaukh, R., Craster, R.V. and Matar, O.K., \textit{Working research codes into fluid dynamics education: a science gateway approach.} Presented at The APS Division of Fluid Dynamics, Denver.\\[0.05cm]

\years{2016}Mudd, S.M., Sinclair, H.D., LeDivellec, T., Dallas, K., \textbf{Grieve, S.W.D.}, \textit{A single event in the Ladakh Himalaya resulted in erosion equivalent to grater than 1000 years of the average erosion rate.} Presented at the BSG Annual General Meeting, Plymouth.\\[0.05cm]

\years{2015}\textbf{Grieve, S.W.D.}, Mudd, S.M., Hurst, M.D., \textit{Constraining hillslope sediment flux using high resolution topographic data.} Presented at the BSG Annual General Meeting, Southampton.\\[0.05cm]

\years{2015}Clubb, F.J., Mudd, S.M., Attal, M., Milodowski, D.T., \textbf{Grieve, S.W.D.}, \textit{The Relationship between Drainage Density, Erosion Rate, and Hilltop Curvature: Implications for Sediment Transport Processes.} Presented at the BSG Annual General Meeting, Southampton.

\subsection*{Poster Presentations}

\years{2024} Hoseason, T.\student, \textbf{Grieve, S.W.D.}, Harvey, G.L, Lines, E.R., \textit{Quantifying topographic variability in forested landscapes.} Presented at the BSG Annual Meeting, Loughborough.\\[0.05cm]

\years{2023}Wu, N.\student, \textbf{Grieve, S.W.D.}, Manning, A.J., Spencer, K.L., \textit{
Flocs as Vectors for Microplastics in the Aquatic Environment.} Presented at the AGU Fall Meeting, San Francisco.\\[0.05cm]

\years{2023}Wu, N.\student, \textbf{Grieve, S.W.D.}, Manning, A.J., Spencer, K.L., \textit{Modelling the Sedimentation of Micro- and Nanoplastics in the Ocean from Surface to Sediment.} Presented at Nanoplastics: Origin, Structure and Fate, Utrecht.\\[0.5cm]

\years{2023}Xue, S.\student, Spencer, K.L., \textbf{Grieve, S.W.D.}, \textit{Erosion Estimation in Coastal Historic Landfills Using Terrestrial Laser Scanning.} Presented at the BSG Annual Meeting, Edinburgh.\\[0.05cm]

\years{2023}Marshall-Hawkes, R., Owen, H.J.F, \textbf{Grieve, S.W.D.}, Lines, E.R., \textit{Bridging the gap between earth observation and forest ecology.} Presented at SilviLaser 2023, London.\\[0.05cm]

\years{2023}Miltiadou, M., \textbf{Grieve, S.W.D.}, Ruiz-Benito, P., Lines, E.R., \textit{Bridging the gap between earth observation and forest ecology.} Presented at SilviLaser 2023, London.\\[0.05cm]

\years{2023}Owen, H.J.F, Noach, A., Allen, M.J.\student, \textbf{Grieve, S.W.D.}, Lines, E.R., \textit{Improved leaf wood classification using deep learning in European Forests.} Presented at SilviLaser 2023, London.\\[0.05cm]

\years{2023}Wu, N.\student, Spencer, K.L. \textbf{Grieve, S.W.D.}, Manning, A.J., \textit{Flocs as Vectors for Microplastics in the Aquatic Environment.} Presented at the Recent Trends in Microplastic Research Meeting, Jena.\\[0.05cm]

\years{2023}\textbf{Grieve, S.W.D.}, Owen, H.J.F., Ruiz-Benito, P., Lines, E.R., \textit{High resolution forest-landscape interactions.} Presented at the EGU General Assembly, Vienna.\\[0.0cm]

\years{2023}Xue, S.\student, Spencer, K.L., \textbf{Grieve, S.W.D.}, \textit{The impacts of climate change on eroding coastal historic landfills.} Presented at the EGU General Assembly, Vienna.\\[0.05cm]

\years{2023} Miltiadou, M. \textbf{Grieve, S.W.D.}, Owen, H.J.F., Ruiz-Benito, P., Lines, E.R., \textit{Fusion of European forest inventories with Sentinel-1 and Sentinel-2 data for improving scalability in estimating forest variables.} Presented at the EGU General Assembly, Vienna.\\[0.05cm]

\years{2022}\textbf{Grieve, S.W.D.}, Trivi\~{n}o, J.T., Astigarraga, J., Owen, H.J.F., Ruiz-Benito, P., Lines, E.R., \textit{Linking forests and landscapes in four dimensions.} Presented at the BSG Annual Meeting, Northumbria.\\[0.05cm]

\years{2021}Allen, M.J.\student, Owen, H.J.F., \textbf{Grieve, S.W.D.}, Lines, E.R., \textit{Automated tree species classification from forest Terrestrial Laser Scanning data.} Presented at the British Ecological Society Annual Meeting, Liverpool.\\[0.05cm]

\years{2021}Xue, S.\student, Spencer, K.L., \textbf{Grieve, S.W.D.}, \textit{A global perspective on the future impacts of brownfield and solid waste disposal sites in the coastal zone.} Presented at ECSA 58 - EMECS 13: Estuaries and coastal seas in the Anthropocene, Online.\\[0.05cm]

\years{2021}Mudd, S.M., Gabet, E.J., Wood, R.W., \textbf{Grieve, S.W.D.}, Binnie, S.A, Dunai, T.J., \textit{Rapidly eroding hilltops are surprisingly smooth: ridgetop curvature varies with the square root of erosion rate.} Presented at vEGU2021: Gather Online.\\[0.05cm]

\years{2020}\textbf{Grieve, S.W.D.}, Mudd, S.M., Clubb, F.J., Singer, M.B., Michaelides, K., Chen, S-a, \textit{Inverting fluvial network topology to understand landscape dynamics.} Presented at EGU2020: Sharing Geoscience Online.\\[0.05cm]

\years{2020}Wheatland, J., Spencer, K.L., \textbf{Grieve, S.W.D.}, Gu, C., Carr, S., Manning, A., Bushby, A., Botto, L. \textit{A New 3D Descriptor for Irregularly Shaped Suspended Sediment Aggregates.} Presented at EGU2020: Sharing Geoscience Online.\\[0.05cm]

\years{2020}Gailleton, B., Mudd, S.M., Clubb, F.J., Hurst, M.D., \textbf{Grieve, S.W.D.}, \textit{Importance of concavity for interpreting rates and patterns of landscape evolution from river profiles.} EGU2020: Sharing Geoscience Online.\\[0.05cm]

\years{2019}Clubb, F.J., Mudd, S.M., \textbf{Grieve, S.W.D.}, Hurst, M.D., Gailleton, B., Milodowski, D.T., Valters, D., Goodwin, G., \textit{LSDTopoTools: open-source software for topographic analysis.} Presented at the AGU Fall Meeting, San Francisco.\\[0.05cm]

\years{2019}\textbf{Grieve, S.W.D.}, Mudd, S.M., Clubb, F.J., Singer, M.B., Michaelides, K., Chen, S-a, \textit{Fingerprinting landscape dynamics through fluvial network topology.} Presented at the BSG Annual General Meeting, Sheffield.\\[0.05cm]

\years{2019}Bourne, A.J., Davis, S.M., Abbott, P.M., \textbf{Grieve, S.W.D.}, \textit{Determining possible controls on Icelandic volcanism during the last glacial period: an examination of the Greenland ice-core tephra framework.} Presented at The 20th Congress of the International Union for Quaternary Research (INQUA) 2019, Dublin.\\[0.05cm]

\years{2019}\textbf{Grieve, S.W.D.}, Hales, T.C., Parker, R.N., Mudd, S.M., Clubb, F.J., \textit{Relationships between zero order basin morphology and sediment transport.} Presented at the EGU General Assembly, Vienna.\\[0.05cm]

\years{2018}Chen, S-a, Michaelides, K., \textbf{Grieve, S.W.D.}, Singer, M.B., \textit{Climatic Controls on River Longitudinal Profiles Globally.} Presented at the AGU Fall Meeting, Washington, D.C.\\[0.05cm]

\years{2018}\textbf{Grieve, S.W.D.}, Hales, T.C., Parker, R.N., Mudd, S.M., Clubb, F.J.,\textit{Understanding the relationship between colluvial hollow morphology and hillslope processes.} Presented at the EGU General Assembly, Vienna.\\[0.05cm]

\years{2017}Clubb, F.J., Mudd, S.M., Hurst, M.D., \textbf{Grieve, S.W.D.}, \textit{Unsteady Landscapes: Fluvial Terraces, Channel Profiles, and Hillslopes at the Mendocino Triple Junction, California.} Presented at the AGU Fall Meeting, New Orleans.\\[0.05cm]

\years{2016}Hales, T.C., Parker, R.N., Mudd, S.M., \textbf{Grieve, S.W.D.}, \textit{How do Colluvial Hollows Fill?} Presented at the AGU Fall Meeting, San Francisco.\\[0.05cm]

\years{2016}Hurst, M.D., \textbf{Grieve, S.W.D.}, Mudd, S.M., \textit{Coupled analysis of hillslope and channel metrics for erosion rates in a tectonically active landscape}. Presented at the AGU Fall Meeting, San Francisco.\\[0.05cm]

\years{2016}\textbf{Grieve, S.W.D.}, Mudd, S.M., Milodowski, D.T., Clubb, F.J., Furbish, D.J., \textit{How does the resolution of topographic data impact the measurement of geomorphic processes?} Presented at the BSG Annual General Meeting, Plymouth.\\[0.05cm]

\years{2016}Mudd, S.M., Hurst, M.D., \textbf{Grieve, S.W.D.}, Milodowski, D.T., Clubb, F.J., Attal, M.\textit{Detecting geomorphic processes and change with high resolution topographic data.} Presented at the EGU General Assembly, Vienna.\\[0.05cm]

\years{2015}Mudd, S.M., \textbf{Grieve, S.W.D.}, Milodowski, D.T., Hurst, M.D., Clubb, F.J., Valters, D.A., \textit{LSDTopoToolBox: Open source geomorphology.} Presented at the BSG Annual General Meeting, Southampton.\\[0.05cm]

\years{2015}Clubb, F.J., Mudd, S.M., Attal, M., Milodowski, D.T., \textbf{Grieve, S.W.D.}, \textit{The Relationship between Drainage Density, Erosion Rate, and Hilltop Curvature: Implications for Sediment Transport Processes}. Presented at the AGU Fall Meeting, San Francisco.\\[0.05cm]

\years{2015}Parker, R.N., Hales, T.C., Mudd, S.M., \textbf{Grieve, S.W.D.}, \textit{Precipitation and soil accumulation history modifies future landslide hazard.} Presented at the AGU Fall Meeting, San Francisco.\\[0.05cm]

\years{2015}Parker, R.N., Hales, T.C., Mudd, S.M., \textbf{Grieve, S.W.D.}, \textit{Climate change has limited impact on soil-mantled landsliding.} Presented at the EGU General Assembly, Vienna.\\[0.05cm]

\years{2014}\textbf{Grieve, S.W.D.}, Mudd, S.M., Hales, T.C., \textit{How long is a hillslope?} Presented at the AGU Fall Meeting, San Francisco.\\[0.05cm]

\years{2014}Mudd, S.M., Attal, M., Milodowski, D.T., \textbf{Grieve, S.W.D.}, Valters, D.A., \textit{A statistical technique for identifying channels of different steepness in transient landscapes.} Presented at the EGU General Assembly, Vienna.\\[0.05cm]

\hrule
\section*{Classroom Teaching Experience (Course Level)}

\years{2023}Individual Research Project, Supervisor (M.Sc.)\\[0.05cm]
\years{2023}Environmental Data Acquisition and Analysis, Lecturer (M.Sc.)\\[0.05cm]
\years{2022}Research Design and Methods, Lecturer (M.Sc.)\\[0.05cm]
\years{2021--}Ideas and Practice in Geography and Environmental Science, Tutor (1st year)\\[0.05cm]
\years{2020}Research Design, Convener (2nd year)\\[0.05cm]
\years{2019--}Advanced Geospatial Science, Convener (3rd year)\\[0.05cm]
\years{2019}Fieldwork in Physical Geography and Environmental Science, Lecturer (1st year)\\[0.05cm]
\years{2019}Progress in Physical Geography and Environmental Science, Lecturer (3rd year)\\[0.05cm]
\years{2019--}Geospatial Science, Lecturer (2nd year)\\[0.05cm]
\years{2018}Environmental Hazards, Lecturer (3rd year)\\[0.05cm]
\years{2018--}Geomorphology, Lecturer, Convener (2nd year)\\[0.05cm]
\years{2018-2023}Geography in the World, Lecturer (1st year)\\[0.05cm]
\years{2018--}Independent Geographical Study/Project in Environmental Science, Supervisor (3rd year)\\[0.05cm]
\years{2017--2018}Research Software Engineering with Python, Lecturer (M.Sc.)\\[0.05cm]
\years{2016}Quantitative Methods in Earth Sciences, Laboratory Demonstrator (3rd year)\\[0.05cm]
\years{2015}Geomorphology, Laboratory Demonstrator and Tutor (2nd year)\\[0.05cm]
\years{2014--2015}Object Oriented Software Engineering Principles, Laboratory Demonstrator (M.Sc.)\\[0.05cm]
\years{2014--2015}Object Orientated Software Engineering: Spatial Algorithms, Laboratory Demonstrator (M.Sc.)\\[0.05cm]
\years{2014--2015}Principles of Geographical Information Science, Laboratory Demonstrator (M.Sc.)\\[0.05cm]
\years{2014--2015}Introduction To Spatial Analysis, Laboratory Demonstrator (M.Sc.)\\[0.05cm]
\years{2014--2015}Distributed GIS, Laboratory Demonstrator (M.Sc.)\\[0.05cm]
\years{2014--2015}Spatial Modelling, Laboratory Demonstrator (M.Sc.)\\[0.05cm]
\years{2014}Earth Surface Systems Course Assistant (1st year) \\[0.05cm]
\years{2014}Fundamental Methods in Geography, Laboratory and Field Demonstrator (2nd year)\\[0.05cm]
\years{2013--2016}Geo-Visualisation, Laboratory Demonstrator (M.Sc.)\\[0.05cm]
\years{2013--2015}Advanced Spatial Database Methods, Laboratory Demonstrator (M.Sc.)\\[0.05cm]
\years{2013--2015}Further Spatial Analysis, Laboratory Demonstrator (M.Sc.)\\[0.05cm]
\years{2013--2014}Earth Surface Systems, Laboratory Demonstrator and Tutor (1st year)\\[0.05cm]

\hrule
\section*{Field Teaching Experience (Course Level)}
\years{2023}Bore Place fieldtrip (1st year)\\[0.05cm]
\years{2022}Getting started in Geography and Environmental Research (1st year)\\[0.05cm]
\years{2017, 2019}Fieldwork in Physical Geography and Environmental Science (1st year)\\[0.05cm]
\years{2014--2015}Cyprus field course (4th year honours)\\[0.05cm]
\years{2014}Fundamental Field Methods in Geography (2nd year)\\[0.5cm]

\hrule
\section*{Service}
\noindent

\years{2025}\textbf{Co-Convener} EGU Session GM2.2, \textit{Novel data, methods and applications in Geomorphometry}. EGU General Assembly, Vienna.\\[0.05cm]
\years{2024}\textbf{Co-Convener} EGU Session GM3.2, \textit{Novel data, methods and applications in Geomorphometry}. EGU General Assembly, Vienna.\\[0.05cm]
\years{2023--}\textbf{Editorial Board Member} Earth Surface Processes and Landforms.\\[0.05cm]
\years{2023--}\textbf{Chair of the Publications and Communications Committee} British Society for Geomorphology.\\[0.05cm]
\years{2023}\textbf{Athena Swan Data Lead} School of Geography, Queen Mary University of London.\\[0.05cm]
\years{2023--}\textbf{IT and Research Infrastructure Board Faculty Representative} Queen Mary University of London.\\[0.05cm]
\years{2021--}\textbf{Director of Graduate Studies (Physical Geography and Environmental Science)} School of Geography, Queen Mary University of London.\\[0.05cm]
\years{2021-2023}\textbf{Managed Research Desktop Advisory Group} Queen Mary University of London.\\[0.05cm]
\years{2021}\textbf{Co-Convener} EGU Session GM2.7, \textit{Advances in geomorphometry and landform mapping: possibilities, challenges and perspectives}. vEGU2021: Gather Online.\\[0.05cm]
\years{2021--}\textbf{Grant Reviewer} NASA Mars Data Analysis Program \\[0.05cm]
\years{2021}\textbf{Ph.D. Examiner}: Thomas Lawrence, \textit{Quantification of Micro-Scale Floc Porosity Characteristics Utilising 3D Microtomography}.\\[0.05cm]
\years{2020-2021}\textbf{Deputy Director of Examinations} School of Geography, Queen Mary University of London.\\[0.05cm]
\years{2019--}\textbf{Panel Member} Software Sustainability Institute Fellowship programme.\\[0.05cm]
\years{2020}\textbf{Judge at NERC DTP Environmental Hackathon.}\\[0.05cm]
\years{2020}\textbf{Co-Convener} EGU Session GM2.1, \textit{Advances in geomorphometry and landform mapping: possibilities, challenges and perspectives}. EGU2020: Sharing Geoscience Online.\\[0.05cm]
\years{2020}\textbf{Co-Convener} EGU Short Course SC1.2, \textit{Testing geoscientific code in Python: what, how, and why you should be doing it}. EGU2020: Sharing Geoscience Online.\\[0.05cm]
\years{2019}\textbf{Convener} EGU Short Course SC1.36, \textit{Making high resolution topographic analysis more reproducible with LSDTopoTools}. EGU General Assembly, Vienna.\\[0.05cm]
\years{2019--}\textbf{Grant Reviewer}: NERC Constructing a Digital environment \\[0.05cm]
\years{2019}\textbf{Ph.D. Examiner}: Gabriel Connor-Streich, \textit{Graph theoretical analysis of braided rivers}.\\[0.05cm]
\years{2018--2020}\textbf{Academic lead on engagement, retention and success} School of Geography, Queen Mary University of London.\\[0.05cm]
\years{2018--}\textbf{Academic Advisor} For B.Sc. Geography and B.Sc. Environmental Science programs at Queen Mary University of London.\\[0.05cm]
\years{2014--}\textbf{Journal Peer Reviewer}: Geological Society of America Bulletin; Geophysical Research Letters; Geomorphology; International Journal of Geographical Information Science; Journal of Geophysical Research: Earth Surface; Water Resources Research; Icarus; Scientific Reports; The Journal of Hydrology; The Journal of Open Source Software; Earth Surface Dynamics; Entropy; Earth Surface Processes and Landforms; Reference Module in Earth Systems and Environmental Sciences \\[0.05cm]
\years{2014--2015}\textbf{Session Chair} M.Sc. GIS postgraduate conference, University of Edinburgh.\\[0.05cm]

\hrule
\section*{Funding Received}
\noindent

\years{2025} College QR Research Fund, University of Lincoln \textit{Landscape Disruptors: Invasive plants as an unquantified risk to landscapes, flooding and infrastructure in a changing world}\\
P.I. Catherine Sanders\\
Co.I. \textbf{Stuart W. D. Grieve}\\
Award: \textbf{£8,850} \\[0.05cm]

\years{2025} ESRC responsive mode: \textit{Critically Green: Tracing the Geopolitical, Social and Environmental Footprints of Military Decarbonisation}\\
P.I. Benjamin Neimark\\
Co.I. \textbf{Stuart W. D. Grieve}\\
Award: \textbf{£782,728} \\[0.05cm]

\years{2024} British Council \textit{Indonesia BMKG PhD Scholarship}\\
Co-Lead \textbf{Stuart W. D. Grieve}\\
Co-Lead \textbf{Cedric John}\\
Award: \textbf{Partnership agreement to fully fund PhDs until 2030} \\[0.05cm]

\years{2024} DERI Events and Sponsorship Fund \textit{The role of 3D data to understand the structure and function of environmental systems}\\
P.I. \textbf{Stuart W. D. Grieve}\\
Award: \textbf{£240} \\[0.05cm]

\years{2024} Royal Society International Exchanges Scheme: \textit{Quantifying the three dimensional structure and function of flocs}\\
P.I. Kate L. Spencer\\
Co.I. \textbf{Stuart W. D. Grieve}\\
Award: \textbf{£7,283} \\[0.05cm]

\years{2021} QMUL Undergraduate Research Bursary Scheme: \textit{Mapping channel head morphology under a changing climate}\\
P.I. \textbf{Stuart W. D. Grieve}\\
Award: \textbf{£1,000} \\[0.05cm]

\years{2021} Code for Science and Society Event Fund: \textit{Reproducible Silicon Landscapes}\\
P.I. \textbf{Stuart W. D. Grieve}\\
Co. I Fiona J. Clubb\\
Award: \textbf{£14,314} \\[0.05cm]

\years{2020} NERC COVID-19 Public Engagement Grant: \textit{ChessWatch: a co-designed online observatory for the River Chess}\\
P.I. Catherine M. Heppell\\
Co. I: \textbf{Stuart W. D. Grieve}\\
Award: \textbf{£10,000} \\[0.05cm]

\years{2020} UKRI Future Leaders Fellowship: \textit{Next generation forest dynamics modelling using remote sensing data}\\
P.I. Emily R. Lines\\
Co. I: \textbf{Stuart W. D. Grieve}\\
Award: \textbf{£1,230,000} \\[0.05cm]

\years{2019} QMUL Strategic Facilities Investment Fund: \textit{A multi-sensor aerial observatory for dynamic characterisation of Earth’s landscapes and ecosystems}\\
P.I.: \textbf{Stuart W. D. Grieve} and Emily R. Lines\\
Award: \textbf{£348,839} \\[0.05cm]

\years{2017}British Society for Geomorphology Outreach Grant: \textit{GeoBus: River in a box}\\
P.I.: \textbf{Stuart W. D. Grieve}\\
Co. I: Charlotte J Pike\\
Award: \textbf{£900} \\[0.05cm]

\years{2014}British Society for Geomorphology Student Travel Grant\\
Award: \textbf{£750} \\[0.05cm]

\years{2014}NERC Cosmogenic Isotope Analysis Facility: \textit{Hillslope-channel coupling in a steady-state landscape.}\\
P.I.: T.C. Hales \\
Co. I.: Simon M. Mudd, Robert N. Parker and \textbf{Stuart W. D. Grieve}\\
Award: \textbf{£19,320} \\[0.05cm]

\years{2013}Safe Software Grant Program\\
Award: \textbf{Software licence for FME Desktop Edition} \\[0.05cm]

\years{2011}SAAS Postgraduate Students’ Allowances Scheme\\
Award: \textbf{£3400} \\[0.05cm]

\years{2011}University of Edinburgh Postgraduate Bursary\\
Award: \textbf{£1300} \\[0.05cm]

\hrule
\section*{Professional Memberships}
\noindent

\years{2020--}Fellow of the Higher Education Academy\\[0.05cm]
\years{2019--}Society of Research Software Engineering\\[0.05cm]
\years{2016--}European Geosciences Union\\[0.05cm]
\years{2014--}American Geophysical Union\\[0.05cm]
\years{2014--}British Society for Geomorphology\\[0.005cm]

\hrule
\section*{Other Qualifications}
\noindent

\years{2022--} UK Civil Aviation Authority A2 UAV Pilot certificate of competence\\[0.05cm]

\end{document}
